Staged Abstract Interpreters

### 2019-04-06 paper/60_cases.tex
paper

\begin{lstlisting}
  type AnsM[T] = RepReaderT[RepStateT[
                   RepStateT[RepSetReaderStateM[Cache, Cache, ?], Time, ?], //Add Time into a RepStateT
                 Store, ?], Env, T]
  type Result = (Rep[Set[(Value, Store, Time)]], Rep[Cache])
\end{lstlisting}

@@

\begin{lstlisting}
  def tick(e: Expr): AnsM[Unit] = for {
    τ <- get_time; u <- liftM(StateTMonad.put((e::τ).take($k$)))
  } yield u
  def alloc(x: String): AnsM[Addr] = for {
    τ <- get_time
  } yield KCFAAddr(x, τ)
\end{lstlisting}

>>>>

\begin{lstlisting}
  type AnsM[T] = RepReaderT[RepStateT[
                   RepStateT[RepSetReaderStateM[Cache, Cache, ?], Time, ?], //add Time into a RepStateT
                 Store, ?], Env, T]
  type Result = (Rep[Set[(Value, Store, Time)]], Rep[Cache])
\end{lstlisting}

@@

\begin{lstlisting}
  def tick(e: Expr): AnsM[Unit] = for {
    τ <- get_time; u <- liftM(StateTMonad.put((e::τ).take($k$)))
  } yield u
  def alloc(x: String): AnsM[Addr] = for {
    τ <- get_time
  } yield unit(KCFAAddr(x, τ)) // we use unit to turn a current-stage constant to next-stage value
\end{lstlisting}

### 2019-04-06 paper/70_eval.tex
paper

\begin{figure}[h]
\tiny
\begin{tabular}{@{}lllll@{}}
\toprule
    program             &\#AST & unstaged   & staged     & $\frac{\text{unstaged}}{\text{staged}}$ \\ \midrule
    @rsa@               & 451  & 0.308      & 0.064      & 459.15\%          \\
    @church@            & 120  & 71.811     & 23.990     & 299.34\%          \\
    @fermat@            & 310  & 0.043      & 0.006      & 716.67\%          \\
    @mbrotZ@            & 331  & 1.112      & 0.214      & 519.63\%          \\
    @lattice@           & 609  & 31.874     & 8.816      & 358.69\%          \\
    @kcfa-worst-16@     & 182  & 0.083      & 0.013      & 638.46\%          \\
    @kcfa-worst-32@     & 358  & 0.452      & 0.044      & 1027.27\%         \\
    @kcfa-worst-64@     & 774  & 3.329      & 0.236      & 1410.59\%         \\
    @solovay-strassen@  & 523  & 5.94       & 1.189      & 428.43\%          \\
    \bottomrule
\end{tabular}
\caption{Evaluation result for 0CFA without store-widening.} \label{evaluation_result}
\end{figure}

Figure~\ref{evaluation_result} shows the evaluation result, comparing the
performance improved by staging on 0CFA without store-widening. The
\textit{unstaged} and \textit{staged} columns show the median time to finish the
analysis (in seconds). The last column $\frac{\text{unstaged}}{\text{staged}}$
shows the improvement from staging. \todo{0cfa, 1cfa, store-widen}
As we can see from the table, the staged version significantly outperforms the
unstaged version on all benchmarks, especially for the @kcfa-worst-@$n$ series.
We observe the most improvement of 14x times faster than the unstaged version on
@kcfa-worst-64@. On average, the staging produces code that run 6x times faster
than the unstaged analyzer.

>>>>

\begin{figure}[h]
\footnotesize
\begin{tabular}{@{}lllll@{}}
\toprule
    program             &\#AST & unstaged   & staged     & $\frac{\text{unstaged}}{\text{staged}}$ \\ \midrule
    @fib@               & 32   & 0.013      & 0.002      & 650.00\%          \\
    @rsa@               & 451  & 0.232      & 0.042      & 552.38\%          \\
    @church@            & 120  & 67.342     & 18.917     & 355.99\%          \\
    @fermat@            & 310  & 0.024      & 0.004      & 600.00\%          \\
    @mbrotZ@            & 331  & 0.763      & 0.127      & 600.79\%          \\
    @lattice@           & 609  & 31.874     & 8.816      & 361.59\%          \\
    @kcfa-worst-16@     & 182  & 0.045      & 0.006      & 750.00\%          \\
    @kcfa-worst-32@     & 358  & 0.284      & 0.022      & 1290.91\%         \\
    @kcfa-worst-64@     & 774  & 2.18       & 0.129      & 1689.92\%         \\
    @solovay-strassen@  & 523  & 5.094      & 1.189      & 428.43\%          \\
    \bottomrule
\end{tabular}
\caption{Evaluation result for 0CFA without store-widening.} \label{evaluation_result}
\end{figure}

Figure~\ref{evaluation_result} shows the evaluation result, comparing the
performance improved by staging on 0CFA without store-widening. The
\textit{unstaged} and \textit{staged} columns show the median time to finish the
analysis (in seconds). The last column $\frac{\text{unstaged}}{\text{staged}}$
shows the improvement from staging. \todo{0cfa, 1cfa, store-widen}
As we can see from the table, the staged version significantly outperforms the
unstaged version on all benchmarks, especially for the @kcfa-worst-@$n$ series.
We observe the most improvement of 17x times faster than the unstaged version on
@kcfa-worst-64@. On average, the staging produces code that run 7x times faster
than the unstaged analyzer.

### 2019-04-06 paper/abstract.tex
paper

As an example of abstraction without regret, we show that staging abstract
interpreters is practical and useful to optimize static analysis while requiring
least engineering efforts and not compromising any soundness. We conduct three
case studies, including a comparison with
\citeauthor{Boucher:1996:ACN:647473.727587}'s abstract compilation,
the applicability on various control-flow analyses, and the use to modular
analysis. We also empirically evaluate the performance improved by staging. The
overhead of the abstraction layers is eliminated in the generated code, and the 
experiment shows an average speedup of 6.6x with staging for control-flow analysis.

>>>>

As an example of abstraction without regret, we show that staging abstract
interpreters is practical and useful to optimize static analysis while requiring
least engineering efforts and not compromising any soundness. We conduct three
case studies, including a comparison with
\citeauthor{Boucher:1996:ACN:647473.727587}'s abstract compilation,
the applicability on various control-flow analyses, and the use to modular
analysis. We also empirically evaluate the performance improved by staging. The
overhead of the abstraction layers is eliminated in the generated code, and the 
experiment shows an average speedup of 7x with staging for control-flow analysis.
